\section{Front assembly}
Front assembly consists of two \href{https://www.maxongroup.com/maxon/view/category/motor?etcc_cu=onsite&etcc_med_onsite=Product&etcc_cmp_onsite=EC+flat+Program&etcc_plc=Overview-Page-Brushless-DC-Motors&etcc_var=%5bcom%5d%23en%23_d_&target=filter&filterCategory=ecflat}{Maxon EC45 Flat} brushless DC motors. The motors have hall sensors and encoders. Power is unknown.

The motors are equipped with Maxon GP42C planetary gearheads.

The 8-pin connector has this pin-out (according to \footnote{\href{https://www.maxongroup.com/medias/sys_master/root/8882563055646/EN-21-297.pdf}{https://www.maxongroup.com/medias/sys\_master/root/8882563055646/EN-21-297.pdf}} and \footnote{\href{https://www.maxongroup.com/medias/sys_master/root/8882567512094/EN-21-310.pdf}{https://www.maxongroup.com/medias/sys\_master/root/8882567512094/EN-21-310.pdf}}):
\begin{itemize}
  \item Pin 1 -- Hall sensor 1
  \item Pin 2 -- Hall sensor 2
  \item Pin 3 -- \verb|+5V|
  \item Pin 4 -- Motor winding 3
  \item Pin 5 -- Hall sensor 3
  \item Pin 6 -- \verb|GND|
  \item Pin 7 -- Motor winding 1
  \item Pin 8 -- Motor winding 2
\end{itemize}

\section{Rear wheel}
The rear wheel is driven by a brushless \href{https://www.goldenmotor.com/magicpie/magicpie.html}{"Magic Pie"}\footnote{\href{https://www.goldenmotor.com/magicpie/magicpie.html}{https://www.goldenmotor.com/magicpie/magicpie.html}} hub motor manufactured by "Golden Motor". It is a 36V model, but not sure what power output.

The hub motor is controlled using a twist throttle and has cruise-control. Cruise control is (de-)activated using the red button above the green button with a horn logo. Pulling the brakes deactivates the cruise-control as well. The cruise-control does not account for wind or slopes, all it does is keep the same current in the motor.

The hub motor also features regenerative braking.
